%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{}
\begin{center}
{\Large Chatbot Platforms}
\end{center}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{frame}[fragile]\frametitle{Bot Building Platforms}
\begin{itemize}
\item Bot building platforms provide tools that help you design unique conversation scenarios, define corresponding actions and analyze interactions.
\item 
They use a mixture of AI and machine learning algorithms to make the bots understand Natural language (NLU—Natural language understanding), process the conversation text and extracts information (NLP—Natural Language Processing) and respond to the user preserving the context of the conversation (NLG—Natural Language Generation).
\end{itemize}

{\tiny (Ref: Chatbots 101 - Architecture \& Terminologies -  Bhavani Ravi)}

\end{frame}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{frame}[fragile]\frametitle{Conversation Platforms}
 Established players
\begin{itemize}
\item Google DialogFlow : https://dialogflow.com
\item Facebook Wit.ai : https://www.wit.ai
\item IBM Watson Assistant : https://www.ibm.com/cloud/watson-assistant/
\item Microsoft LUIS : https://www.luis.ai/
\item Amaon Lex : https://aws.amazon.com/lex
\item SAP Conversational AI : https://recast.ai
\item RASA : https://www.rasa.com/
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]\frametitle{}
\begin{center}
{\Large Why Rasa?}
\end{center}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{frame}[fragile]\frametitle{Local Models}
\begin{itemize}
\item Many chatbot platforms are currently available, from rudimentary rule-based AIML (Artificial Intelligence Markup Language), to highly sophisticated AI bots. 
\item Some popular chatbot platforms are API.ai, Wit.ai, Facebook APIs, Microsoft LUIS, IBM Watson, etc.
\item RASA-NLU builds a local NLU (Natural Language Understanding) model for extracting intent and entities from a conversation. It’s open source, fully local and above all, free! 
\item It is also compatible with wit.ai, LUIS, or api.ai, so you can migrate your chat application data into the RASA-NLU model.
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{frame}[fragile]\frametitle{Security}
\begin{itemize}
\item Enterprises (and their customers) want AI assistants, not FAQ chatbots, but they’re difficult to build; if you’re not Google, and that is where Rasa comes in.
\item Fully controlling and owning your IP and data is crucial, and can’t be done using cloud APIs. In the age of GDPR, HIPAA companies run Rasa on-premise or in a private cloud.
\end{itemize}

{\tiny (Ref: Our Open Source Community Is Growing Faster than Ever. Weren't Chatbots Meant to Be Dead? - Rasa Community Update - Alexander Weidauer )}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{frame}[fragile]\frametitle{Control}
\begin{itemize}
\item You don't have to hand over your data to FB/MSFT/GOOG
\item You don't have to make a https call to parse every message.
\item You can tune models to work well on your particular use case.
\end{itemize}
\end{frame}
